The effect of changing news frames

### 2022-06-28 pres/20211007/PSAI_20211009.tex
Update pres as well
pray

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usetheme[]{Frankfurt}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Hypodermic needle after all? Individual-level Moderators of Media Framing Effects},
  pdfauthor={Nicolai Berk\^{}*},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Hypodermic needle after all? Individual-level Moderators of Media
Framing Effects}
\subtitle{Presentation at EPSIP Colloquium, HU Berlin}
\author{Nicolai Berk\(^*\)}
\date{May 3rd, 2021}
\institute{\(^*\)RTG Dynamics/Humboldt Universität zu Berlin}

@@

\hypertarget{media-effects---maximal-or-minimal}{%
\subsection{Media effects - maximal or
minimal?}\label{media-effects---maximal-or-minimal}}

\begin{frame}[allowframebreaks]{Media effects - maximal or minimal?}
\center

\includegraphics[width=0.4\textwidth,height=\textheight]{vis/volksempfanger.jpg}
\includegraphics[width=0.4\textwidth,height=\textheight]{vis/ufo_scares.jpg}

\flushleft

@@

Maximal paradigm also follows from classic work

\begin{itemize}
\tightlist
\item
  attitude instability (Converse 1962; Zaller 1992)
\item
  framing (Nelson, Clawson, and Oxley 1997)
\item
  agenda-setting (McCombs and Shaw 1972)
\end{itemize}

\center

\includegraphics[width=0.3\textwidth,height=\textheight]{vis/mineff.png}

\flushleft

@@

\(\rightarrow\) strong effects unlikely

@@

Evidence seems to support both views:
\end{frame}

\begin{frame}{strong media effects on:}
\protect\hypertarget{strong-media-effects-on}{}
\begin{itemize}
\tightlist
\item
  voting behaviour (Boomgaarden and Vliegenthart 2009; Devine and Murphy
  2020; Ladd and Lenz 2009),
\item
  issue agenda (King, Schneer, and White 2017),
\item
  attitudes (Nelson, Clawson, and Oxley 1997; Foos and Bischof 2020)
\end{itemize}
\end{frame}

\begin{frame}{weak or no effects on:}
\protect\hypertarget{weak-or-no-effects-on}{}
\begin{itemize}
\tightlist
\item
  voting behaviour (Gentzkow, Shapiro, and Sinkinson 2011),
\item
  issue agenda (Lau, Rogers, and Love 2021),
\item
  attitudes (Guess et al. 2021).
\end{itemize}
\end{frame}

\hypertarget{moderators}{%
\section{Moderators}\label{moderators}}

\hypertarget{towards-a-theory-of-conditioning-factors}{%
\subsection{Towards a theory of conditioning
factors}\label{towards-a-theory-of-conditioning-factors}}

\begin{frame}{Towards a theory of conditioning factors}
Recently more discussion of moderators

\begin{itemize}
\tightlist
\item
  Mostly based on expectations regarding source:

  \begin{itemize}
  \tightlist
  \item
    Discounting of biased news (Chiang and Knight 2011)
  \item
    Rejection of partisan takeovers (Spirig 2020)
  \end{itemize}
\item
  facing biased new media outlets doesn't seem to affect citizens (Guess
  et al. 2021)
\end{itemize}
\end{frame}

\hypertarget{open-questions}{%
\subsection{Open questions:}\label{open-questions}}

\begin{frame}{Open questions:}
\begin{itemize}
\tightlist
\item
  What about outlets currently consumed changing their commentary?
\item
  What about individual-level factors?

  \begin{itemize}
  \tightlist
  \item
    political knowledge, opinion strength (Zaller 1992)?
  \item
    media diet (Bennett and Iyengar 2008)?
  \item
    partisan identification (Taber and Lodge 2006)?
  \end{itemize}
\item
  Is attitude change a result of changing issue definitions (Ajzen and
  Fishbein 2000; Nelson, Clawson, and Oxley 1997)?
\end{itemize}
\end{frame}

\hypertarget{the-case}{%
\section{The case}\label{the-case}}

\begin{frame}{The case}
\begin{itemize}
\tightlist
\item
  In fall of 2015, major German tabloid Bild started calling for support
  for incoming refugees.
\item
  This was a major deviation from the papers' agitative history.
\end{itemize}

\includegraphics{vis/BildFlüchtlingskinder.png}

\includegraphics{vis/BildNot.png}
\end{frame}

\hypertarget{onwards-the-framing-changed}{%
\subsection{2016 onwards the framing
changed}\label{onwards-the-framing-changed}}

\begin{frame}{2016 onwards the framing changed}
\center

\includegraphics[width=\textwidth,height=0.5\textheight]{vis/UebermedienBild2.png}
\end{frame}

\hypertarget{logic-of-the-paper}{%
\subsection{Logic of the paper}\label{logic-of-the-paper}}

\begin{frame}{Logic of the paper}
\begin{itemize}
\tightlist
\item
  I argue this represents a natural experiment to study migration
  framing,
\item
  allowing to identify the \emph{causal} impact of news framing on:

  \begin{itemize}
  \tightlist
  \item
    migration opinions,
  \item
    and issue definitions.
  \end{itemize}
\item
  especially interesting case:

  \begin{itemize}
  \tightlist
  \item
    instead of treatment with a new source (Guess et al. 2021),
    cue-taking (from the newspaper) can be expected.
  \item
    expectation of change in bias among readers unlikely (Chiang and
    Knight 2011; Spirig 2020)
  \end{itemize}
\end{itemize}

\emph{\(\rightarrow\) strong expectations for framing effect!}
\end{frame}

\hypertarget{data-and-research-design}{%
\section{Data and research design}\label{data-and-research-design}}

\hypertarget{the-gles-offers-a-number-of-possible-data-sources}{%
\subsection{The GLES offers a number of possible data
sources:}\label{the-gles-offers-a-number-of-possible-data-sources}}

\begin{frame}{The GLES offers a number of possible data sources:}
\begin{itemize}
\tightlist
\item
  Longterm-tracking,

  \begin{itemize}
  \tightlist
  \item
    N \(\approx\) 1000,
  \item
    four times/year,
  \item
    2009-17
  \end{itemize}
\item
  Panel,

  \begin{itemize}
  \tightlist
  \item
    N \(>\) 10,000,
  \item
    clustered around election
  \end{itemize}
\end{itemize}

Both regularly contain questions on

\begin{itemize}
\tightlist
\item
  news consumption,
\item
  migration/integration attitudes,
\item
  open-ended MIP.
\end{itemize}
\end{frame}

\hypertarget{treatments-and-field-dates}{%
\subsection{Treatments and Field
Dates}\label{treatments-and-field-dates}}

\begin{frame}[allowframebreaks]{Treatments and Field Dates}
Journalists ascribe change to changing editors. This leaves us with a
total of 4 possible treatments:

\begin{enumerate}
\tightlist
\item
  Summer of 2015
\item
  Diekmann replaced as editor-in-chief by Tanit Koch in 2016,
\item
  Diekmann finally left Bild in February 2017,
\item
  Koch replaced by Julian Reichelt in January 2018.
\end{enumerate}

Not entirely clear which treatment is relevant -\textgreater{} assess
changing framing in the newspaper!

@@

\includegraphics{vis/gles_treatments.png}
\end{frame}

\hypertarget{treatment-selection}{%
\subsection{Treatment selection}\label{treatment-selection}}

\begin{frame}{Treatment selection}
\begin{enumerate}
\item
  Pre-select migration content with supervised classifier.
\item
  Several possible approaches for treatment identification:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  inductive frame identification (FA/STM)
\item
  dictionary for frames (humanitarian/crime/\ldots)
\item
  sentiment towards migration
\end{itemize}

\begin{enumerate}
\setcounter{enumi}{2}
\tightlist
\item
  Treatment identified where parallel paths diverge
\end{enumerate}
\end{frame}

\hypertarget{modelling}{%
\subsection{Modelling}\label{modelling}}

\begin{frame}{Modelling}
Diff-in-Diff:

\center

\[ y = \beta_1 * T + \beta_2 * B + \beta_3 * T * B \]

\begin{itemize}
\tightlist
\item
  DVs: migration attitudes \& issue definitions
\item
  Additional interactions for individual-level moderators.
\end{itemize}
\end{frame}

\hypertarget{measuring-issue-definitions}{%
\subsection{Measuring issue
definitions}\label{measuring-issue-definitions}}

\begin{frame}{Embedding regression (Rodriguez, Spirling, and Stewart
2020)}
\protect\hypertarget{embedding-regression-rodriguez2020}{}
\begin{itemize}
\tightlist
\item
  applicable in low-N environments.
\item
  pre-existing word embeddings to understand how different groups
  communicate about migration.
\item
  assess associations with migration in the MIP answers.
\end{itemize}
\end{frame}

\hypertarget{fin}{%
\subsection{Fin}\label{fin}}

\begin{frame}{Fin}
\center \Large Thank you for your attention!
\end{frame}

@@

\hypertarget{a-preliminary-effort-at-sentiment-identification}{%
\subsection{A preliminary effort at sentiment
identification}\label{a-preliminary-effort-at-sentiment-identification}}

\begin{frame}[allowframebreaks]{A preliminary effort at sentiment
identification}
\begin{itemize}
\tightlist
\item
  identify sentences mentioning terms from migration dictionary.
\item
  estimate sentiment of these sentences with German BERT sentiment
  classifier (Guhr et al. 2020).
\item
  Trained to classify a variety of German text (wiki, reviews, tweets,
  \ldots) into positive, neutral, and negative content
\end{itemize}

\includegraphics{vis/comparative_sentiment_migration.png}

@@

However, unclear what this really measures:

\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs2.png}
\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs3.png}

\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs4.png}
\includegraphics[width=0.45\textwidth,height=\textheight]{vis/BERTProbs5.png}

Takeaways:

\begin{itemize}
\tightlist
\item
  wait for supervised coding.
\item
  focus on specific frames.
\item
  measure association.
\end{itemize}
\end{frame}

@@

\hypertarget{resources-1}{%
\subsection*{Resources}\label{resources-1}}
\addcontentsline{toc}{subsection}{Resources}

\begin{frame}[allowframebreaks]{Resources}
\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Ajzen2000}{}%
Ajzen, Icek, and Martin Fishbein. 2000. {``{Attitudes and the
Attitude-Behavior Relation: Reasoned and Automatic Processes}.''}
\emph{European Review of Social Psychology} 11 (1): 1--33.
\url{https://doi.org/10.1080/14792779943000116}.

@@

@@

\leavevmode\hypertarget{ref-Devine2020}{}%
Devine, Daniel, and Justin Murphy. 2020. {``{Does Media Coverage Drive
Public Support for UKIP or Does Public Support for UKIP Drive Media
Coverage?}''} \emph{British Journal of Political Science} 50 (3):
893--910. \url{https://doi.org/10.1017/S0007123418000145}.

@@

@@

\leavevmode\hypertarget{ref-Guhr2020}{}%
Guhr, Oliver, Anne Kathrin Schumann, Frank Bahrmann, and Hans Joachim
Böhme. 2020. {``{Training a broad-coverage German sentiment
classification model for dialog systems}.''} \emph{LREC 2020 - 12th
International Conference on Language Resources and Evaluation,
Conference Proceedings}, no. May: 1627--32.

\leavevmode\hypertarget{ref-King2017}{}%
King, Gary, Benjamin Schneer, and Ariel White. 2017. {``{How the news
media activate public expression and influence national agendas}.''}
\emph{Science} 358 (November): 776--80.
\url{https://doi.org/10.1007/978-1-349-11336-1_13}.

\leavevmode\hypertarget{ref-Ladd2009a}{}%
Ladd, Jonathan Mc Donald, and Gabriel S. Lenz. 2009. {``{Exploiting a
rare communication shift to document the persuasive power of the news
media}.''} \emph{American Journal of Political Science} 53 (2):
394--410. \url{https://doi.org/10.1111/j.1540-5907.2009.00377.x}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usetheme[]{Frankfurt}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The effect of changing news frames},
  pdfauthor={Nicolai Berk\^{}*},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\AtBeginSection{}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{The effect of changing news frames}
\subtitle{Presentation at the 2021 Annual Conference of the Political
Studies Association of Ireland}
\author{Nicolai Berk\(^*\)}
\date{Oct 9th, 2021}
\institute{\(^*\)RTG Dynamics/Humboldt Universität zu Berlin}

@@

\begin{frame}{Motivation}
\center

\includegraphics[width=0.4\textwidth,height=\textheight]{vis/volksempfanger.jpg}
\end{frame}

\hypertarget{literature-and-theory}{%
\section{Literature and Theory}\label{literature-and-theory}}

\begin{frame}[allowframebreaks]{Media effects - maximal or minimal?}
\protect\hypertarget{media-effects---maximal-or-minimal}{}
Maximal paradigm also follows from classic work:

\begin{itemize}
\tightlist
\item
  attitude instability (Converse 1962; Zaller 1992)
\item
  agenda-setting (McCombs and Shaw 1972)
\item
  framing (Nelson, Clawson, and Oxley 1997)
\end{itemize}

@@

@@

\(\rightarrow\) strong effects unlikely
\end{frame}

\begin{frame}[allowframebreaks]{Empirical evidence}
\protect\hypertarget{empirical-evidence}{}
\begin{block}{Evidence for large effects}
\protect\hypertarget{evidence-for-large-effects}{}
\begin{itemize}
\tightlist
\item
  Framing effects found in experimental data (Busby, Flynn, and Druckman
  2019; Leeper and Slothuus 2020).
\item
  Newspaper slant affects attitudes (Foos and Bischof 2020).
\item
  Salience and tonality of migration news affects attitudes (Boomgaarden
  and Vliegenthart 2009).
\end{itemize}
\end{block}

\begin{block}{Evidence for no/weak effects}
\protect\hypertarget{evidence-for-noweak-effects}{}
\begin{itemize}
\tightlist
\item
  Newspaper slant has no effect on attitudes (Gentzkow, Shapiro, and
  Sinkinson 2011; Guess et al. 2021; Štětka, Mihelj, and Tóth 2020).
\item
  Newspaper takeovers have no effect on attitudes (Durante and Knight
  2012; Spirig 2020).
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Synthesis}
\protect\hypertarget{synthesis}{}
\textbf{When} can we expect strong media effects?

\begin{itemize}
\tightlist
\item
  Many current approaches test media effects of different outlets
  (Gentzkow, Shapiro, and Sinkinson 2011; Guess et al. 2021).
\item
  However, \textbf{news consumers discount bias and take cues from
  outlets}.

  \begin{itemize}
  \tightlist
  \item
    Baum and Gussin (2008) show that consumers take heuristics about
    content bias from outlet brands.
  \item
    Chiang and Knight (2011) show that outlet bias moderates the effect
    of candidate endorsements.
  \end{itemize}
\end{itemize}

\(\rightarrow\) \textbf{within-outlet changes} in content most likely
cases to observe media effects.
\end{frame}

\begin{frame}[allowframebreaks]{Emphasis framing}
\protect\hypertarget{emphasis-framing}{}
\textbf{What kind of changes should matter?}

\begin{itemize}
\tightlist
\item
  I draw on literature on

  \begin{itemize}
  \tightlist
  \item
    the \textbf{value-expectancy} framework (Ajzen and Fishbein 2000).
  \item
    and \textbf{emphasis framing} (Leeper and Slothuus 2020; Nelson,
    Clawson, and Oxley 1997).
  \end{itemize}
\item
  Argues that issue attitudes are a product of \textbf{associated
  considerations}.
\end{itemize}

@@

\includegraphics{vis/CognitiveStorage.png}
\end{frame}

\hypertarget{empirical-strategy}{%
\section{Empirical strategy}\label{empirical-strategy}}

\begin{frame}{The case: Germany 2017}
\protect\hypertarget{the-case-germany-2017}{}
\begin{itemize}
\tightlist
\item
  First election after 2015 refugee movements.
\item
  Radical-right challenger party enters parliament, center loses.
\item
  Migration top of the agenda.
\end{itemize}

\(\rightarrow\) constantly strong attention to migration,

\(\rightarrow\) good case to study effects of framing.
\end{frame}

\begin{frame}{Design}
\protect\hypertarget{design}{}
\begin{itemize}
\tightlist
\item
  Collect 2.5M articles from major German newspapers.
\item
  Classify according to migration content.
\item
  Identify emphasis frames.
\item
  Correlate changes in framing with changes in attitudes.
\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{Issue attitudes and news consumption}
\protect\hypertarget{issue-attitudes-and-news-consumption}{}
\begin{itemize}
\tightlist
\item
  Panel data from the German Longitudinal Election Study (GLES 2019).
\item
  Contains questions on news consumption and immigration and integration
  attitudes.
\item
  6 waves in 2017, containing both items.
\item
  Immigration attitude measured on a 7-point Likert scale:

  \begin{itemize}
  \tightlist
  \item
    ``\emph{Immigration should be made easier (-3) or restricted (3)}.''
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{Migration content}
\protect\hypertarget{migration-content}{}
\begin{itemize}
\tightlist
\item
  Pre-assign likelihoods for migration content using extended migration
  dictionary.
\item
  Draw stratified sample of 1,800 articles, hand-code.
\item
  Fine-tune German BERT deep-learning classifier.
\item
  Performs very well: F1: 0.94, recall: 0.93, precision: 0.95.
\item
  13.5k out of 400k articles in 2017 about migration (3.5\%)
\end{itemize}

@@

\includegraphics{vis/salience_papers.png}
\end{frame}

\begin{frame}[allowframebreaks]{Migration framing}
\protect\hypertarget{migration-framing}{}
\begin{itemize}
\tightlist
\item
  Estimate 60-topic structural topic model (Roberts et al. 2014), using
  date and paper as covariates.
\item
  Annotate.
\item
  Select relevant frames with clear expectations regarding attitudinal
  effects.
\end{itemize}

\textbf{Topics}:

\begin{itemize}
\tightlist
\item
  Capital crime (sexual assault/rape/murder) committed by refugees,
\item
  illegal entry and petty crime,
\item
  refugee numbers,
\item
  labour market needs for and job market integration of refugees,
\item
  deportations,
\item
  internment camps (e.g.~Moria),
\item
  drownings in the Mediterranean.
\end{itemize}

\includegraphics{vis/frames_papers_pres.png}
\end{frame}

\begin{frame}{Estimation}
\protect\hypertarget{estimation}{}
\emph{Two models}:

\begin{itemize}
\tightlist
\item
  OLS of aggregate Difference-in-Differences (DiDs).
\item
  Individual-level model with 2-way fixed effects.
\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{DiD-model}
\protect\hypertarget{did-model}{}
\[y = \beta_1*W + \beta_2*R + \beta_3*W*R\]

\centering

\includegraphics[width=0.5\textwidth,height=\textheight]{vis/Illustration_of_Difference_in_Differences.png}

\begin{itemize}
\tightlist
\item
  Estimate change in newspaper framing and attitudes among readers from
  one wave to another, controlling for shifts in other newspapers/reader
  groups.
\item
  Regress opinion shift among readership on shift in newspaper attention
  to different frames.
\item
  Better identified (exact change \emph{beyond} general trend),
\item
  but framing not individually matched.
\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{2-way FE model}
\protect\hypertarget{way-fe-model}{}
\begin{itemize}
\tightlist
\item
  Individual estimate of frame attention for each respondent, according
  to newspaper read.
\item
  Regress opinion on exposure to each frame,
\item
  controlling for wave and individual fixed-effects.
\end{itemize}

\begin{itemize}
\tightlist
\item
  Individual estimates,
\item
  but explains \emph{all} variation beyond

  \begin{itemize}
  \tightlist
  \item
    time-independent individual factors and
  \item
    general trends across time,
  \item
    including random individual deviations.
  \end{itemize}
\end{itemize}
\end{frame}

\hypertarget{preliminary-results}{%
\section{Preliminary results}\label{preliminary-results}}

\begin{frame}{Preliminary results}
Different specifications:

\begin{itemize}
\tightlist
\item
  all readers/exclusive readers of one newspaper,
\item
  different lags to measure exposure (1 day, 1 week, 1 month, half a
  year),
\item
  immigration and integration attitude as dependent variable.
\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{Difference-in-Difference model}
\protect\hypertarget{difference-in-difference-model}{}
\includegraphics{vis/frame_effects_did.png}
\end{frame}

\begin{frame}{Fixed-effect model}
\protect\hypertarget{fixed-effect-model}{}
\includegraphics{vis/frame_effects_fe.png}
\end{frame}

\begin{frame}{Preliminary conclusion}
\protect\hypertarget{preliminary-conclusion}{}
\begin{itemize}
\tightlist
\item
  No effects of media framing even in most-likely case.
\item
  \emph{However}, many possible explanations:

  \begin{itemize}
  \tightlist
  \item
    Measurement issues,
  \item
    Issue-sorting in 2015, subsequent ``digging in,''
  \item
    too little variation in dependent.
  \end{itemize}
\end{itemize}

\(\rightarrow\) further work necessary\ldots{}
\end{frame}

\begin{frame}{Further hypotheses}
\protect\hypertarget{further-hypotheses}{}
\begin{itemize}
\tightlist
\item
  Motivated reasoning and polarisation (Taber and Lodge 2006).
\item
  Readers respond by changing outlet (Arceneaux and Johnson 2013).
\item
  Mobilisation, not attitudinal change (Gentzkow, Shapiro, and Sinkinson
  2011; Štětka, Mihelj, and Tóth 2020).
\end{itemize}
\end{frame}

\begin{frame}{To-do's up next}
\protect\hypertarget{to-dos-up-next}{}
\begin{itemize}
\tightlist
\item
  Clump frames together for holistic picture.
\item
  Estimate effect on readership, attitude polarisation, and AfD-support.
\item
  Natural experiment (again)?
\end{itemize}
\end{frame}

\begin{frame}{Fin}
\protect\hypertarget{fin}{}
\centering

\emph{Thank you!}
\end{frame}

@@

\begin{frame}[allowframebreaks]{Variation dependent variable}
\protect\hypertarget{variation-dependent-variable}{}
\centering

\includegraphics{vis/imm_readers_pres.png}

@@

\centering

\includegraphics{vis/DiD_model_ps_immint.png}
\end{frame}

\begin{frame}[allowframebreaks]{Salience}
\protect\hypertarget{salience}{}
\includegraphics{vis/salience_papers_focus.png}
\end{frame}

\begin{frame}[allowframebreaks]{Framing attention}
\protect\hypertarget{framing-attention}{}
\includegraphics{vis/frames_papers_focus_pres.png}
\end{frame}

\begin{frame}{Specifications DiD}
\protect\hypertarget{specifications-did}{}
\centering

\includegraphics[width=0.7\textwidth,height=\textheight]{vis/effectplot_frames_did.png}
\end{frame}

\begin{frame}{Specifications 2-way FE}
\protect\hypertarget{specifications-2-way-fe}{}
\centering

\includegraphics[width=0.7\textwidth,height=\textheight]{vis/effectplot_frames_fe_abs.png}
\end{frame}

@@

\begin{frame}[allowframebreaks]{Resources}
\protect\hypertarget{resources-1}{}
\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Ajzen2000}{}%
Ajzen, Icek, and Martin Fishbein. 2000. {``{Attitudes and the
Attitude-Behavior Relation: Reasoned and Automatic Processes}.''}
\emph{European Review of Social Psychology} 11 (1): 1--33.
\url{https://doi.org/10.1080/14792779943000116}.

\leavevmode\hypertarget{ref-Arceneaux2013}{}%
Arceneaux, Kevin, and Martin Johnson. 2013. \emph{{Changing Mind or
Changing Channels? Partisan News in an Age of Choice}}. University of
Chicago Press.

\leavevmode\hypertarget{ref-Baum2008}{}%
Baum, Matthew A., and Phil Gussin. 2008. {``{In the Eye of the Beholder:
How Information Shortcuts Shape Individual Perceptions of Bias in the
Media}.''} \emph{Quarterly Journal of Political Science} 3 (1): 1--31.
https://doi.org/\url{http://dx.doi.org/10.1561/100.00007010}.

@@

\leavevmode\hypertarget{ref-Busby2019}{}%
Busby, Ethan, D. J. Flynn, and James N. Druckman. 2019. {``{Studying
Framing Effects on Political Preferences}.''} \emph{Doing News Framing
Analysis II}, 27--50. \url{https://doi.org/10.4324/9781315642239-2}.

@@

\leavevmode\hypertarget{ref-Durante2012}{}%
Durante, Ruben, and Brian Knight. 2012. {``{Partisan control, media
bias, and viewer responses: Evidence from berlusconi's italy}.''}
\emph{Journal of the European Economic Association} 10 (3): 451--81.
\url{https://doi.org/10.1111/j.1542-4774.2011.01060.x}.

@@

\leavevmode\hypertarget{ref-GLES2019LongTermTracking}{}%
GLES. 2019. {``{Longterm-Online-Tracking 2009-2017 (GLES)}.''} Cologne:
GESIS Data Archive.
https://doi.org/\url{https://doi.org/10.4232/1.13416}.

@@

\leavevmode\hypertarget{ref-Leeper2020}{}%
Leeper, Thomas J., and Rune Slothuus. 2020. {``{How the News Media
Persuades}.''} \emph{The Oxford Handbook of Electoral Persuasion},
150--68. \url{https://doi.org/10.1093/oxfordhb/9780190860806.013.4}.
